\chapter{基础理论}

Some of the greatest \emph{discoveries} in science werer made by accident.

\textit{Some of the greatest \emph{discoveries} in science were made by accident.}

\textbf{Some of the greatest \emph{discoveries} in science were made by accident.}

In physics, the mass-energy equivalence is stated by the equation $E=mc^2$, discovered
in 1905 by Albert Einstein.

The mass-energy equivalence is described by the famous equation 

$$E=mc^2$$

discovered in 1905 by Albert Einstein.
In natural units($c = 1$), the formula expresses the identity

\begin{equation}
E=m
\end{equation}

Subscripts in math mode are written as $a_b$ and superscripts are written as $a^b$. 
These can be combined an nested to write expressions such as

$$T^{i_1 i_2 \dots i_p}_{j_1 j_2 \dots j_q} = T(x^{i_1},\dots,x^{i_p},e_{j_1},\dots,e_{j_q})$$

We write integrals using $\int$ and fractions using $\frac{a}{b}$. 
Limits are placed on integrals using superscripts and subscripts:

$$\int_0^1 \frac{1}{e^x} =  \frac{e-1}{e}$$

Lower case Greek letters are written as $\omega$ $\delta$ etc. 
while upper case Greek letters are written as $\Omega$ $\Delta$.

Mathematical operators are prefixed with a backslash as $\sin(\beta)$, $\cos(\alpha)$, $\log(x)$ etc.

Lich涉及许多底层理论和系统，包括并行计算和分布式系统，操作系统，文件系统，数据库系统，网络，还包括相应的底层硬件架构。
需要对数据结构和算法，有良好基础。所以，对基本问题和理论，要有清晰和深入的掌握，才能“运用之妙，存乎一心”。

存储中一些重要的问题，可以借助AI的力量去解决。智能存储，不仅仅是口号，更是技术进步的必要趋势。

按道法术器组织结构，写成大文章。

常用优化原则：
\begin{itemize}
    \item 局部性
    \item 并行
    \item 聚合，批处理
    \item 延迟
\end{itemize}

\section{学习计划}

\begin{itemize}
    \item SCSI
    \item NVMe
    \item SPDK
\end{itemize}

\section{Distributed System}
\section{Parallel Computing}
